PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 0.8$

### 2014-10-22 qfenv_paper/qf_environment.tex
Added some Peng+2010 description to text

In Figure \ref{fig:qffit_comp}, we plot  best-fit parameterization of
$f_{\rm{red}}$ for high and low density environment from zCOSMOS,
\cite{Iovino:2010aa} (square) and \cite{Kovac:2014aa} (triangle), and
SDSS, \cite{Baldry:2006aa} (diamond) and \cite{geha12a} (cross). From
\cite{Iovino:2010aa} we calculate $f_{\rm{red}} = 1-f_{\rm{blue}}$
using the best-fit $f_{\rm{blue}}$ from the mass bin $\mathcal{M} =
10^{10.3} - 10^{10.8} \mathcal{M}_{\odot}$. From \cite{Kovac:2014aa}
we plot an estimated $f_{\rm{Q}}$ by applying the residual between SFR
based and color based galaxy classifications to the best-fit
$f_{\rm{red}}$ at $\mathcal{M} = 10^{10.5} \mathcal{M}_{\odot}$ for
low ($\delta = 0.0$) and high density environments ($\delta =
1.5$). Similarly, from \cite{Baldry:2006aa} we plot $f_{\rm{Q}}$
derived from the best-fit $f_{\rm{red}}$ at $\mathcal{M} = 10^{10.5}
\mathcal{M}_{\odot}$ for low ($\delta = 0.0$) and high density
environment ($\delta = 1.0$). For \cite{geha12a}, we plot $f_{\rm{Q}}$
for their isolated galaxy sample in their mass bin closest to $10^{10.5} \mathcal{M}_{\odot}$, $\mathcal{M} = 10^{10.55} \mathcal{M}_{\odot}$.

@@

>>>>

In Figure \ref{fig:qffit_comp}, we plot  best-fit parameterization of
$f_{\rm{red}}$ for high and low density environment from SDSS (panel a), \cite{Baldry:2006aa} (diamond) and \cite{geha12a} (cross), zCOSMOS (panel b),
\cite{Iovino:2010aa} (empty square) and \cite{Kovac:2014aa} (triangle), and \cite{Peng:2010aa} (filled square; panel c) from both surveys. From
\cite{Iovino:2010aa} we calculate $f_{\rm{red}} = 1-f_{\rm{blue}}$
using the best-fit $f_{\rm{blue}}$ from the mass bin $\mathcal{M} =
10^{10.3} - 10^{10.8} \mathcal{M}_{\odot}$. From \cite{Kovac:2014aa}
we plot an estimated $f_{\rm{Q}}$ by applying the residual between SFR
based and color based galaxy classifications to the best-fit
$f_{\rm{red}}$ at $\mathcal{M} = 10^{10.5} \mathcal{M}_{\odot}$ for
low ($\delta = 0.0$) and high density environments ($\delta =
1.5$). Similarly, from \cite{Baldry:2006aa} we plot $f_{\rm{Q}}$
derived from the best-fit $f_{\rm{red}}$ at $\mathcal{M} = 10^{10.5}
\mathcal{M}_{\odot}$ for low ($\delta = 0.0$) and high density
environment ($\delta = 1.0$). For \cite{geha12a}, we plot $f_{\rm{Q}}$
for their isolated galaxy sample in their mass bin closest to $10^{10.5} \mathcal{M}_{\odot}$, $\mathcal{M} = 10^{10.55} \mathcal{M}_{\odot}$. Finally for \cite{Peng:2010aa}, we plot the parameterized $f_{\rm{red}}$ at $\mathcal{M} = 10^{10.5} \mathcal{M}_{\odot}$ using the specified best-fit parameters in low ($\delta =0.0$) and high ($\delta = 1.4$) density environments.

@@

%\cite{Peng:2010aa} computes the comoving density field for the SDSS DR7 and zCOSMOS galaxies in order to calculate $f_{\mathrm{red}}$ as a function of mass and environment. If we compare our $f_{\mathrm{Q}}$ to the best-fit parameterization $f_{\mathrm{red}}$ for their SDSS subsample we find that
